\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-08-16 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

According to the Ministry of Housing and Urban-Rural Development in China, the proportion of second-hand housing transactions rose to 37.1\% in 2023, with this trend showing continuous growth. Unlike the primary housing market, where transactions are straightforward, the secondary housing market necessitates sellers having access to buyers, thereby making transaction costs a critical factor for both parties. In this context, real estate brokers play a pivotal role in mitigating these costs. They provide essential market information, negotiation support, and legal assistance, thereby facilitating smoother and more efficient transactions in the real estate market. The involvement of brokers reduces the information asymmetry and transactional frictions that are characteristic of the secondary housing market, thus enhancing market efficiency.

With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous. Moreover, it is not merely a matter of legal improvement, as in the past, the intermediary market was quite chaotic, with individuals being able to set up a brokerage business without any qualifications. Nowadays, the government has taken steps to regulate the disorderly conduct of intermediaries through administrative and legal measures, leading to a more standardized and orderly market environment. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communications between buyers and sellers \citep{glaeser_real_2017}. Given the heterogeneous and "thin" nature of real estate goods \citep{HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.

@@

Additionally, in the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction. However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers. In a perfectly competitive market, sellers would be indifferent in their choice of real estate agents. Nonetheless, as the market trends toward increased monopolistic competition, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.

While the co-listing strategy—listing properties with multiple brokerages—has been suggested as beneficial in some markets, such as under a multiple-listing service \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, it is suboptimal within China's real estate context for several reasons. First, exclusive contracts between sellers and agents typically preclude co-listing, thereby limiting its feasibility. Second, although sellers can list with multiple brokerages, smaller agencies often lack a sufficient client base, reducing their effectiveness. Third, engaging multiple brokers can dilute agent incentives due to perceived competition, leading to less proactive efforts. Finally, while agency service cost differences exist, these costs are relatively minor compared to the property's value and are more closely related to the financial risks involved. Consequently, risk-averse sellers tend to prefer agencies offering a guaranteed service level. Moreover, \citet{bergemann_data_2024} finds that when platforms possess significant bargaining power, co-listing with multiple agents is no more efficient than listing with a single agent.

Given the dual nature of online promotion and offline transactions in the real estate brokerage industry, the quality of offline services is crucial for influencing client decisions. This principle underpins Lianjia's strategy of establishing numerous stores within targeted communities. By opening a wide range of stores in various neighborhoods and adopting a downstream consolidation model through platform design, the brokerage effectively attracts sellers to list their properties and buyers through its extensive platform resources. This strategy not only enhances transaction volume but also increases income derived from these transactions.

In this paper, we empirically estimate the effects of offline store clustering and online platform consolidation in China's second-hand real estate market. Utilizing micro-level transaction data, we construct our research sample by aggregating information at the neighborhood level. We employ a regression discontinuity design (RDD) to identify the optimal influential radius of offline stores on neighborhood transactions, finding that this radius corresponds to a brokerage's five-minute walk service distance, which is also documented in similar fields \citep{AZMI2012406}. Subsequently, we apply a difference-in-difference (DID) estimation method to evaluate the exogenous impact of Lianjia's market entry on local segments. This exogenous effect captures the clustering impact of offline real estate brokerage stores. Our results indicate that Lianjia's offline stores significantly enhance transaction revenues, although this effect diminishes during and after the COVID-19 period.

To evaluate the effects of platform-mediated consolidation, we consider the year Lianjia implemented its platform-mediated consolidation strategy as an exogenous shock to the market. This strategy primarily revolves around the ACN framework of Lianjia and the incorporation of various franchise stores into the network. Our empirical analysis indicates that this strategy significantly increases revenues and enhances the attraction of buyers and sellers, particularly in the number of house tours facilitated by the brokerage. However, our findings suggest that the platform-mediated consolidation does not effectively reduce the transaction period nor does it promote price concessions. This contrasts with the offline expansion strategy, which demonstrates a positive impact on promoting price concessions. While the economic impact of the online-based consolidation strategy is not as pronounced as that of the offline expansion strategy, it remains economically significant.

@@

Regarding the transaction period, the influence of the offline store is consistently insignificant. This finding suggests that the entry of offline stores does not facilitate the matching of buyers and sellers in the housing market. This outcome aligns with the intuition that when platform and online information is readily accessible, individuals' search behavior tends to be predominantly online-based. Lastly, regarding price concessions, the entry of Lianjia's offline stores exhibits a 4.5\% positive effect. This suggests that the presence of offline stores may facilitate an increase in price concessions. This effect can be attributed to the enhanced efficiency in matching buyers with suitable properties, thereby encouraging sellers to be more amenable to price negotiations. Additionally, offline stores possess better control over neighborhood information, which aids in effectively marketing properties to potential buyers, thereby capturing additional surplus.

To verify the robustness of our results, we calculated the Herfindahl-Hirschman Index (HHI) for each segmented market, defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage. Higher HHI values indicate greater market concentration. To further validate the entry effect, we classified the sample into three groups based on HHI values: low HHI ($0 \leq HHI \leq 1,000$), moderate HHI ($1,000 \leq HHI \leq 2,500$) and high HHI ($2,500 \leq HHI \leq 10,000$). This classification allows us to assess the impact of Lianjia's entry across markets with varying levels of competition and concentration, ensuring that our findings are not driven by specific market conditions. The results, presented in Table \ref{tab:entry_effect_robustness_1}, indicate that the income effect for Lianjia remains consistent across both groups. Specifically, income increases by 7.9\% during the entry period, with the effect decreasing to 5.0\% in the subsequent period for the lower HHI group, which demonstrates the entry can create a very large impact on the compettive market. Moreover, the income increases by 6.8\% and 7.8\% during the entry period and decreases to insignificant after the entry period in the moderate and high concentration market. This demonstrates that Lianjia's entry can only make companies profitable in less competitive markets, and it can enhance profitability in more competitive markets. However, a significant difference emerges in the number of house tours. The entry of Lianjia increases the number of house tours by 5.4\% in the second year and 5.9\% in the third year for the low competitive group. The entry's effect is also significant, with a 3.9\% increase in the number of house tours in the second year for the high concentration market. However, this effect diminishes for the moderately competitive group. The result indicates that the results indicate that when facing other competitors in the market, Lianjia is more likely to make greater efforts to attract more sellers. This analysis underscores the varying impacts of market concentration on Lianjia's market performance post-entry.

>>>>

In recent years, the secondary housing market in China has seen significant growth, with the proportion of second-hand housing transactions rising to 37.1\% in 2023, according to the Ministry of Housing and Urban-Rural Development. This growing market presents unique challenges compared to the primary housing market, primarily due to the necessity for sellers to connect with buyers, making transaction costs a critical factor. Real estate brokers play a pivotal role in mitigating these costs by providing essential market information, negotiation support, and legal assistance, thus facilitating smoother and more efficient transactions. The evolution of China's legal and regulatory framework has significantly impacted the real estate brokerage market, leading to increased standardization and a more orderly market environment. However, despite these improvements, the market remains characterized by offline-dominated transactions, where brokers' expertise and local market knowledge are indispensable due to the persistent information asymmetry. Given the heterogeneous and "thin" nature of real estate goods \citep{glaeser_real_2017, HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.

@@

In China's real estate market, brokerages predominantly operate under a bilateral agency model, where sellers are incentivized to select agencies that can maximize transaction speed and sale price. This agency selection process reflects the strategic behavior of sellers seeking to optimize outcomes within the competitive dynamics of the market. This decision is complicated by the inherent asymmetric information characteristic of real estate markets, which hinders sellers' ability to effectively communicate and connect with potential buyers. In a perfectly competitive market, sellers would theoretically be indifferent in their choice of real estate agents. However, as the market increasingly exhibits traits of monopolistic competition, sellers face a strategic choice: they can either engage a larger brokerage firm, which, despite commanding higher fees, offers the potential for quicker transactions due to superior market reach and resources, or they may opt for a smaller brokerage, which might charge lower fees but could be less efficient in facilitating transactions.

This decision-making process is consistent with the theoretical framework proposed by \citep{bergemann_data_2024}, which examines the dynamics of platforms operating in markets characterized by product heterogeneity and significant market power. According to this framework, platforms can use their informational advantages and market power to attract higher quality sellers with lower listing prices by offering more favorable terms, such as more buyers. This ability to discriminate among sellers based on the quality of their offerings not only enhances the competitive position of the platform, but also contributes to more efficient market outcomes by aligning incentives between sellers and the platform.

Nevertheless,  it is of the importance for the platform to meticulously evaluate the multihoming strategies that are utilized by the sellers. While the co-listing approach—where properties are listed with multiple brokerages—has been demonstrated to yield positive outcomes in certain markets, particularly those utilizing a multiple-listing service \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, it has been shown to be suboptimal in the context of China's real estate market for several reasons. Firstly, exclusive contracts between sellers and agents typically preclude co-listing, thereby limiting its feasibility. Secondly, although sellers are permitted to list with multiple brokerages, smaller agencies frequently lack an adequate client base, which consequently diminishes their efficacy. Thirdly, engaging multiple brokers can result in a dilution of agent incentives due to the perception of competition, which may lead to a reduction in proactive efforts. Finally, while there are differences in the costs of agency services, these costs are relatively minor in comparison to the value of the property and are more closely related to the financial risks involved. Consequently, risk-averse sellers tend to prefer agencies that offer a guaranteed level of service. Furthermore, \citet{bergemann_data_2024} finds that when platforms possess significant bargaining power, co-listing with multiple agents is no more efficient than listing with a single agent.\footnote{The original paper employs an off-platform transaction, yet the concept can be extended to encompass other brokerages in this context.}

In the dual-natured environment of China's real estate brokerage industry, where online promotion and offline transactions are intertwined, the quality of offline services plays a pivotal role in influencing client decisions. This principle informs Lianjia's strategic approach, which entails the establishment of a dense network of storefronts within targeted neighborhoods. By proliferating stores across various neighborhoods and integrating a downstream consolidation model through platform design, Lianjia effectively capitalizes on its extensive resources to attract both sellers and buyers. This strategy not only boosts transaction volumes but also enhances the brokerage's revenue streams from these transactions, underscoring the importance of offline service quality in a market increasingly dominated by large, powerful platforms.

In this paper, we empirically estimate the effects of offline store clustering and online platform consolidation in China's second-hand real estate market. Utilizing micro-level transaction data, we construct our research sample by aggregating information at the neighborhood level. We employ a regression discontinuity design (RDD) to identify the optimal influential radius of offline stores on neighborhood transactions, finding that this radius corresponds to a brokerage's five-minute walk service distance, which is also documented in similar fields \citep{AZMI2012406}. Subsequently, we apply a difference-in-difference (DID) estimation method to evaluate the exogenous impact of Lianjia's market entry on local segments. This exogenous effect captures the clustering impact of offline real estate brokerage stores. The results demonstrate that Lianjia's offline stores markedly augment transaction revenues, although this impact wanes during and in the aftermath of the COVID-19 pandemic. Furthermore, the expansion of offline stores has been found to significantly increase the extent of price concessions, a result that is consistent with the findings of \citep{bergemann_data_2024}, where the bargaining power of the platform was found to be positively correlated with the pricing strategies employed by the seller.

In order to evaluate the effects of platform-mediated consolidation, it is essential to consider the year in which Lianjia implemented its consolidation strategy, as this can be viewed as an exogenous shock to the market. This strategy, which was based on Lianjia's ACN framework, entailed the integration of a diverse range of franchise stores into its network. The empirical analysis demonstrates that this consolidation strategy led to a notable increase in revenues and enhanced the platform's appeal to both buyers and sellers, particularly by facilitating a greater number of house tours through the brokerage. Nevertheless, the analysis indicates that platform-mediated consolidation did not result in an immediate reduction in the transaction period or the promotion of price concessions in the short term. The notable impact on price concessions became evident after two periods following the consolidation, in alignment with Lianjia's offline expansion strategy, which exerted a positive influence on price concessions. This delayed impact can be attributed to the continued role of offline stores in the transaction process. In the initial stages, online advertisements may not be an effective means of attracting buyers. However, as the network expands and more buyers and sellers place their trust in the platform, the benefits become more pronounced. The integration of offline stores enhances the platform's bargaining power vis-à-vis sellers, as these physical locations are instrumental in converting buyer interest into completed transactions and consolidating the platform's market influence.

@@

Regarding the transaction period, the influence of the offline store is consistently insignificant. This finding suggests that the entry of offline stores does not facilitate the matching of buyers and sellers in the housing market. This outcome aligns with the intuition that when platform and online information is readily accessible, individuals' search behavior tends to be predominantly online-based. Lastly, regarding price concessions, the entry of Lianjia's offline stores exhibits a 4.5\% positive effect. This suggests that the presence of offline stores may facilitate an increase in price concessions. This effect can be attributed to the enhanced efficiency in matching buyers with suitable properties, thereby encouraging sellers to be more amenable to price negotiations. This also suggests that brokerages may be able to leverage improved bargaining power with sellers, potentially leading to enhanced transaction outcomes. Additionally, offline stores possess better control over neighborhood information, which aids in effectively marketing properties to potential buyers, thereby capturing additional surplus.

To verify the robustness of our results, we calculated the Herfindahl-Hirschman Index (HHI) for each segmented market, defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage. Higher HHI values indicate greater market concentration. To further validate the entry effect, we classified the sample into three groups based on HHI values: low HHI ($0 \leq HHI \leq 1,000$), moderate HHI ($1,000 \leq HHI \leq 2,500$) and high HHI ($2,500 \leq HHI \leq 10,000$). This classification allows us to assess the impact of Lianjia's entry across markets with varying levels of competition and concentration, ensuring that our findings are not driven by specific market conditions. The results, presented in Table \ref{tab:entry_effect_robustness_1}, indicate that the income effect for Lianjia remains consistent across both groups. Specifically, income increases by 7.9\% during the entry period, with the effect decreasing to 5.0\% in the subsequent period for the lower HHI group, which demonstrates the entry can create a very large impact on the compettive market. Moreover, the income increases by 6.8\% and 7.8\% during the entry period and decreases to insignificant after the entry period in the moderate and high concentration market. This demonstrates that Lianjia's entry can only make companies profitable in less competitive markets, and it can enhance profitability in more competitive markets. However, a significant difference emerges in the number of house tours. The entry of Lianjia increases the number of house tours by 5.4\% in the second year and 5.9\% in the third year for the low competitive group. The entry's effect is also significant, with a 3.9\% increase in the number of house tours in the second year for the high concentration market. However, this effect diminishes for the moderately competitive group. The results suggest that Lianjia is more likely to intensify its efforts to attract a larger number of sellers when faced with increased market competition. As the number of sellers listing with Lianjia increases, the brokerage is able to attract a greater number of buyers and offer better services. By leveraging this expanded customer base, Lianjia is able to enhance its bargaining power over sellers, which in turn allows for greater price concessions in final transactions, ultimately benefiting the platform's overall competitive position in the market and increases total welfare.
